Eco-evolutionary dynamics of finite populations from first principles

### 2023-04-13 ind_files/04_field_eqns.tex
Correct minor typo

We can now use the same trick we used in deriving \eqref{nD_Price_time_dependent} from \eqref{nD_replicator_mutator}. By multiplying both sides of equation \eqref{cts_replicator_mutator} by a type level quantity\footnote{This is now a real function $f(x,t):\mathcal{T} \times [0,infty) \to \mathbb{R}$ of two variables, the trait value and time. I assume this function is nice enough for all the below operations to make sense} $f(x,t)$ and integrating over the trait space, we obtain

>>>>

We can now use the same trick we used in deriving \eqref{nD_Price_time_dependent} from \eqref{nD_replicator_mutator}. By multiplying both sides of equation \eqref{cts_replicator_mutator} by a type level quantity\footnote{This is now a real function $f(x,t):\mathcal{T} \times [0,\infty) \to \mathbb{R}$ of two variables, the trait value and time. I assume this function is nice enough for all the below operations to make sense} $f(x,t)$ and integrating over the trait space, we obtain
